PANCHANGE_analysis

### 2020-09-17 PANCHANGE_analysis.Rmd
adding tidy and glance models summaries

# Questionnaire comparions

@@

```{r gad percentage plot retro_prepan sum}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    labels = c("Baseline", "Prepandemic", "Retrospective")
    )
```

@@

Retro-baseline analyses
Exclude individuals with NA for MHD, age, gender
```{r exclusion criteria for retro-baseline analysis}
dat.retro <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data"))
  )

@@

# 1. Calculate mean change per group

@@

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD prepan Model 0a}
gad_prepan_model0a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1a}
gad_prepan_model1a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1b}
gad_prepan_model1b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1a}
phq_prepan_model1a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1b}
phq_prepan_model1b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1a}
gad_prepan_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1b}
gad_prepan_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1a}
phq_prepan_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1b}
phq_prepan_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1a}
gad_retro_model1a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1b}
gad_retro_model1b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

>>>>

# 1. Questionnaire comparions: Calculate mean change per group

@@

```{r gad percentage plot retro_prepan sum}
dat.long.gad.sum %>%
#  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.sum_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
 #   labels = c("Baseline", "Prepandemic", "Retrospective")
    )
```

@@

Retro-baseline analyses
++CH: need to discuss exclusion criteria
Exclude individuals with NA for MHD, age, gender

```{r Exclusion criteria}

```

```{r exclusion criteria for retro-baseline analysis}
dat.retro <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data"))
  )

@@

@@

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD prepan Model 0a}
# Model
gad_prepan_model0a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(gad_prepan_model0a)

# Regression statistics
gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0a_reg_stats)
gad_prepan_model0a_reg_stats

# Estimate summary table
gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0a_estimates)
gad_prepan_model0a_estimates
```

@@

summary(gad_prepan_model0b)

# Regression statistics
gad_prepan_model0b_reg_stats <- glance(gad_prepan_model0b) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0b_reg_stats)
gad_prepan_model0b_reg_stats

# Estimate summary table
gad_prepan_model0b_estimates <- tidy(gad_prepan_model0b) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
      "depressive_disordersDepressive disorder" = "Depressive disorders",
      "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
      "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
      "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
      "eating_disordersEating disorder" = "Eating disorders",
      "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
      "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
      "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
      "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
      "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
      "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
      "mhd.personality_disorderPersonality disorder" = "Personality disorder"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0b_estimates)
gad_prepan_model0b_estimates
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1a}
gad_prepan_model1a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1a)

# Regression statistics
gad_prepan_model1a_reg_stats <- glance(gad_prepan_model1a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model1a_reg_stats)
gad_prepan_model1a_reg_stats

# Estimate summary table
gad_prepan_model1a_estimates <- tidy(gad_prepan_model1a) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
      "Gender_collapsedFemale" = "Female",
      "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
      "age_category_collapsed19-25" = "19-25 years",
      "age_category_collapsed26-35" = "26-35 years",
      "age_category_collapsed36-45" = "36-45 years",
      "age_category_collapsed46-55" = "46-55 years",
      "age_category_collapsed56-65" = "56-65 years",
      "age_category_collapsed66-70" = "66-70 years",
      "age_category_collapsed71-75" = "71-75 years",
      "age_category_collapsed76+" = "76+ years",
      "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
      "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
      "Ethnicity_collapsedAfrican or African British" = "African or African British",
      "Ethnicity_collapsedOther" = "Other ethnicity",
      "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
    #    "z score",
    "p value"
  )

kable(gad_prepan_model1a_estimates)
gad_prepan_model1a_estimates
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1b}
gad_prepan_model1b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1a}
phq_prepan_model1a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1b}
phq_prepan_model1b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1a}
gad_prepan_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1b}
gad_prepan_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1a}
phq_prepan_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1b}
phq_prepan_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1a}
gad_retro_model1a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1b}
gad_retro_model1b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)
